Plant-pollintor networks worldwide are composed by the same specific building

### 2021-06-02 Draft/Draft.Rmd
Adding motif categories of Simmons 2021 Fun.Ecol.

ggplot(NULL) + 
  geom_point(data = d %>% filter(motif != 1),
             aes(y=as.factor(motif), x=percentil_sizeclass, 
                 color = as.factor(motif)),
             position = "jitter",alpha=0.5)+
  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=mean-SE, xmax=mean+SE), 
                width=1.0,size=1)+
  geom_point(data = motif_means,aes(y = as.factor(motif), x=mean), 
                size=2)+
  labs(y="Motif", x = "Percentile")+
  theme_bw()+
  theme(legend.position = "none")

>>>>

#Add categories based on path length set by Simmons 2021 et al., Functional Ecology
d$Broad_categories[d$motif==2 | d$motif==7 | d$motif==17 | d$motif==3|d$motif==4|d$motif==8] <- "Fan"

d$Broad_categories[d$motif==15 | d$motif==11] <- "Medium-weak"

d$Broad_categories[d$motif==6 | d$motif==16 |  d$motif==12] <- "Strong"

d$Broad_categories[d$motif==5 | d$motif==9 |  d$motif==14|  d$motif==13|  d$motif==10] <- "Weak"

ggplot(NULL) + 
  geom_point(data = d %>% filter(motif != 1),
             aes(y=as.factor(motif), x=percentil_sizeclass, 
                 color = as.factor(Broad_categories)),
             position = "jitter",alpha=0.5)+
  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=mean-SE, xmax=mean+SE), 
                width=1.0,size=1)+
  geom_point(data = motif_means,aes(y = as.factor(motif), x=mean), 
                size=2)+
  labs(y="Motif", x = "Percentile",colour="Motif classification")+
  theme_bw()
